Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 Background/lang_aff.tex
need to cut down 13 lines more woohoo

\begin{sloppypar}
From our preliminary testing of Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
\end{sloppypar}
%\input{Background/ruby.tex}

>>>>

\begin{sloppypar}
From our preliminary testing, Ruby's built-in \texttt{Net::SMTP} library also has an \ehi vulnerability (not documented on the library's homepage).
%A working code sample of the vulnerability, written in Ruby 2.0.0 (the latest stable version at the time of writing), is shown in Listing~\ref{code:rubyemi}.
\end{sloppypar}
%\input{Background/ruby.tex}

### 2016-10-25 Results/fuzz_result.tex
need to cut down 13 lines more woohoo

%\subsection{Fuzzed Data and Received \Emails}

Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
\input{Results/fuzzed_data}

\noindent\textbf{\Email received from forms.} The \emails that we
received can be categorized into two categories. (1) \Emails due to
regular payload: This represents the total number of web applications
that sent \emails to us. This indicates that we were able to
successfully submit the forms on these sites to trigger the web
application to send an \email. (2) \Emails due to malicious payload:
Once we receive an \email from a web application due to the regular
payload, we fuzz those forms with the malicious payloads. This field
represents the total number of unique URLs that are contain an \ehi
vulnerability.

>>>>

%Table~\ref{tab:fuzzed_data} shows the quantity of \emails that we received for the benign and malicious payloads. 
%\input{Results/fuzzed_data}
%
%\noindent\textbf{\Email received from forms.} The \emails that we
%received can be categorized into two categories. (1) \Emails due to
%regular payload: This represents the total number of web applications
%that sent \emails to us. This indicates that we were able to
%successfully submit the forms on these sites to trigger the web
%application to send an \email. (2) \Emails due to malicious payload:
%Once we receive an \email from a web application due to the regular
%payload, we fuzz those forms with the malicious payloads. This field
%represents the total number of unique URLs that are contain an \ehi
%vulnerability.

### 2016-10-25 Results/pre_result.tex
updated for WWW paper
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
need to cut down 13 lines more woohoo

\subsection{Collected Data}

% TODO: Need to put in a number here, and discuss the high level
% crawl. - DONE

From our extensive crawl of the web, we were able to gather the data
shown in Table~\ref{tab:data}. We ran the system for 76 days, during which our system crawled \urls unique URLs,
and found a total of \forms\ forms from \uniqueforms\ unique domains. Out of these forms, our system
found \emailforms\ forms that contained an \email field, from \uniqueemailforms\ unique domains.

\input{data}

>>>>

From our extensive crawl of the web, we were able to gather the data
shown in Table~\ref{tab:data}. We ran the system for 76 days, during which our system crawled \urls unique URLs,
and found a total of \forms\ forms from \uniqueforms\ unique domains. Out of these forms, our system
found \emailforms\ forms that contained an \email field, from \uniqueemailforms\ unique domains.
Table~\ref{tab:fuzzed_data} shows the quantity of \emails we received for the benign and malicious payloads. 
\input{data}
\input{Results/fuzzed_data}

\noindent\textbf{\Email received from forms.} The \emails that we
received can be categorized into two categories. (1) \Emails due to
regular payload: This represents the total number of web applications
that sent \emails to us. This indicates that we were able to
successfully submit the forms on these sites to trigger the web
application to send an \email. (2) \Emails due to malicious payload:
Once we receive an \email from a web application due to the regular
payload, we fuzz those forms with the malicious payloads. This field
represents the total number of unique URLs that are contain an \ehi
vulnerability.

### 2016-10-25 System/components.tex
need to cut down 13 lines more woohoo

\subsubsection{Data Gathering}
\label{Comp:Crawler}
We used an open-source Apache Nutch based Crawler~\cite{nutch}. The \texttt{Crawler} provides the system with a continuous feed of URLs and the HTML contained in those pages. 
\label{Comp:FP}
The \texttt{Form Parser} is responsible for parsing the HTML and retrieving data about the HTML
forms on the page, including the following: (1) Form attributes, such
as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
Data about the form input fields, such as their attributes, names, and
default values. The default values are essential for fields like
{\lstinline{<input type="hidden">}} as these fields are usually used
to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection
module. It has the following functions: (1) Retrieve new forms and
ensure no duplication occurs before the fuzzing stage, (2) reconstruct
each form, using the stored form data, specifically the input fields
and their values, and (3) construct the target URL for the
\texttt{action} attribute of the form to create an HTTP request to the
correct URL for fuzzing.

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:

\noindent\textbf{Non-Malicious Payload.}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \lstinline|reguser(xxxx)@example.com|, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

\noindent\textbf{Malicious Payload.}
After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability. We inject the form parameters with the \texttt{bcc} (blind carbon copy) header. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.

@@

We created four different malicious payloads. Each of these payloads
is crafted for a particular use case. The four payloads are:
(1) nuser(xxxx)@example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com,
(2) nuser(xxxx)@\-example.com\textbackslash{}n\-bcc:\-maluser\-(xxxx)\-@example.com\textbackslash{}n\-x-check:in,
(3) nuser(xxxx)@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.com,
and (4) nuser(xxxx)\-@example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser(xxxx)\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.

Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field. Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications. Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.

@@

\noindent\textbf{Analyzing regular e-mail.}
\sloppy
`Regular \email' refers to the \emails received by account {\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

@@

\noindent\textbf{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser(xxxx)@example.com}} or {\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

>>>>

\subsubsection{Data Gathering}
\label{Comp:Crawler}
We used an open-source Apache Nutch based Crawler~\cite{nutch}. The \texttt{Crawler} provides the system with a continuous feed of URLs and the HTML contained in those pages. 
\label{Comp:FP}
The \texttt{Form Parser} is responsible for parsing the HTML and retrieving data about the HTML
forms on the page, including the following: (1) Form attributes, such
as \texttt{method} and \texttt{action} (URL) for the HTTP request, (2)
Data about form inputs, such as their attributes, names, and
default values. The default values are essential for fields like
{\lstinline{<input type="hidden">}} as these fields are usually used
to check for the submission of forms by bots, and (3) Presence of the {\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted (if the \texttt{action} attribute is a relative URL).

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection
module. It has the following functions: (1) Retrieve forms and
ensure no duplication occurs before the fuzzing stage, (2) reconstruct
each form's input fields
and values, using the stored form data, and (3) construct the target URL
to create an HTTP request for fuzzing.

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer interacts directly with the external web applications. The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{httpperf}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:

\noindent\textbf{Non-Malicious Payload.}
The non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \lstinline|reguser#@example.com|, where \texttt{\#} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

\noindent\textbf{Malicious Payload.}
After receiving an \email from a specific form, we use the malicious payload to try to exploit an \ehi vulnerability. We inject the form fields with the \texttt{bcc} (blind carbon copy) header. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.

@@

We created four different malicious payloads. Each of these payloads
is crafted for a particular use case. The four payloads are:
(1) nuser\#@example.com\textbackslash{}n\-bcc:\-maluser\-\#\-@example.com,
(2) nuser\#@\-example.com\textbackslash{}n\-bcc:\-maluser\-\#\-@example.com\textbackslash{}n\-x-check:in,
(3) nuser\#@\-example.com\textbackslash{}r\textbackslash{}n\-bcc:\-maluser\#\-@example.com,
and (4) nuser\#\-@example.com\-\textbackslash{}r\textbackslash{}n\-bcc:\-maluser\#\-@example.\-com\textbackslash{}r\textbackslash{}n\-x-check:in.

Payload 1 is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field. Payload 2 contains the additional \texttt{x-check} header to inject Python-based web applications. Payloads 3 and 4 are added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems~\cite{rfc2616}. The \# are replaced by an internal id, for mapping to the forms.

% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.

@@

\noindent\textbf{Analyzing regular e-mail.}
\sloppy
`Regular \email' refers to the \emails received by account {\lstinline{reguser#@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

@@

\noindent\textbf{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the {\lstinline{nuser#@example.com}} or {\lstinline{maluser#@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer}.

### 2016-10-25 introduction.tex
need to cut down 13 lines more woohoo

Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (a SQL query in the case of SQL Injection and JavaScript code in the case of Cross-Site Scripting). Developers of web applications must use the correct sanitization routine in all paths leading from user input to a command.

@@

To shed light on this little-studied vulnerability class, we describe
\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
measurement, we crawled the web, extracted forms with \email fields,
and injected them with different payloads to infer the existence of an
\ehi vulnerability. We then audited received \emails to see if any of
the injected data was present. This allowed us to classify whether a
particular URL was vulnerable to the attack. Our automated system
works in a black-box manner, without looking at the web application's
source code, and only analyzes the paylods of the \emails.
%TODO Adam: Added a line to make clear that we wanted a quantification before attempting something like a source-code analyzer. This addresses reviewer 690B's concerns.

>>>>

Many common and well-known web application vulnerabilities, such as SQL Injection and Cross-Site Scripting~\cite{OWASPT10}, are command injection vulnerabilities~\cite{commandinjection}, where malicious user input is used to alter the structure of a command (SQL query and JavaScript code respectively). Developers of web applications must use the correct sanitization routine in all paths leading from user input to a command.

@@

To shed light on this little-studied vulnerability class, we describe
\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
measurement, we crawled the web, extracted forms with \email fields,
and injected them with different payloads to infer the existence of an
\ehi vulnerability. We then audited received \emails to see if any of
the injected data was present. This allowed us to classify whether a
particular URL was vulnerable to the attack. Our automated system
works in a black-box manner, without looking at the web application's
source code, and only analyzes the payloads of the \emails.

### 2016-10-25 rel_work.tex
Currently at 11 total pages. Major paper shrink. Shrank most fonts on most of the tables, eliminated a lot of superfulious code examples and tables. Also removed most \paragraph and \itemize usage, as they were wasting space.
need to cut down 13 lines more woohoo

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).

>>>>

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes the vulnerability. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).
